The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-25 paper/ms.tex
and stellar properties too
rename
fixes

We initially run the Stellar Parameter Classification \citep[SPC:][]{spc} code to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax. For deriving abundances, \teff is fixed from the results of an initial SPC fit, while \logg is fixed to the seismic values. The spectroscopic parameters $v_{\text{mic}}$, and broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile) as well as [Fe/H] and all chemical abundances are derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}.

>>>>

We initially run the Stellar Parameter Classification \citep[SPC:][]{spc} code to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax. For deriving abundances, \teff is fixed from the results of an initial SPC fit, while \logg is fixed to the seismic values. The spectroscopic parameters $v_{\text{mic}}$, and broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile) as well as [Fe/H] and all chemical abundances are derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}, and the results from this calculation are displayed in Table~\ref{stellar_props}. Individual elemental abundances are extracted both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}. The results of these calculations are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}. We note that no abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample.

\input{stellar_props.tex}

\input{abundances_1.tex}
\input{abundances_2.tex}
\input{abundances_3.tex}
